---
title: "BA exploratory analysis"
author: "MJ, EHS, HM"
date: "created: 10/14/2020, last updated: `r format(Sys.time(), '%d %B, %Y')`"
output: html_document
editor_options: 
  chunk_output_type: console
---
#Setup
```{r setup, include=FALSE}
#Clean environment
rm(list = ls())
#Load packages
pacman::p_load(readr,dplyr,lme4,lmerTest,mgcv,tidyverse, scales)

#Load data
data <- read_csv("data.csv")
```

#Exploratory Analyses 1:
Testing the post hoc hypothesis that for the seed colors that converges in the opporsite direction, might converge towards their prototypical binary hues instead of the prototypical unique hue pairings

Preproces
```{r}
#Defining all the hue angles
#Binary hues
purple <- 250.6
orange <- 43.1
chartreuse <- 80.9
cyan <- 165.2
#Hues of each seed color 
dark_rose <- 327.55
mustard <- 49.85
grass_green <- 117.98
ocean_blue <- 179.34
#Hues of each focal color 
red <- 12.2 + 360
yellow <- 62.4
green <- 136.5
blue <- 193.6

#Calculating deltas for appendix 5
#dark rose pairs
dark_rose - purple
red - dark_rose

#mustard pairs
mustard - orange
yellow - mustard

#grass green pairs
grass_green - chartreuse
green - grass_green

#ocean blue pairs
ocean_blue - cyan
blue - ocean_blue

#Creating the binary hue pair and RHAD 2
data <- data %>% 
  mutate(Binary_hue = case_when(
          Color_label_matched == "seed mustard" ~ orange,
          Color_label_matched == "seed grass green" ~ chartreuse,
          Color_label_matched == "seed ocean blue" ~ cyan,
          Color_label_matched == "seed dark rose" ~ purple)) %>% 
  mutate(
    Dif2 = Hue_matched - Binary_hue,
    RHAD2 = 100/(Seed - Binary_hue)*Dif2
  )

#Danish only
danish <- data %>% filter(Language == "Danish")

#Descriptive stats
stats_hue2 <- danish %>% 
  group_by(Color_label_matched, Condition) %>% 
  summarise(max(RHAD2),min(RHAD2), mean(RHAD2), sd(RHAD2), mean(Binary_hue))

```

Analysis:
Using the same individual color model as for the main analysis (see post-hoc analysis section in thesis)
```{r}
model4 <- lmer(
  RHAD2 ~ Generation:Color_label_matched + 
  (1 + Generation + Condition + Generation:Condition| Chain) +
  (1 + Generation + Condition + Generation:Condition| Chain:Subject), 
  data = danish, 
  REML = T, 
  control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10, 
    xtol_abs = 1e-10,
    maxeval = 10000
  )))

summary(model4)

```
Interpretations:
Dark rose had a significantly negative slope (β = -2.01, p < 0.05), displaying convergence in the hypothesized direction.
Grass green yielded non-significant results
Ocean blue and mustard revealed significantly positive slopes (ocean blue: β = 2.9, p < 0.01; mustard: β = 4.1, p < .001), suggesting convergence away from the alternative prototypical hue pairing

#Exploratory Analyses 2:
Prdicting Error rates (not done)
```{r}
pacman::p_load(ggpubr, NCmisc, RColorBrewer, unikn)
#Increased levels of confidence predicts accuracy
# Descriptive
stats_acc <- data %>% 
  group_by(Gender, Color_label_matched) %>% 
  summarise(min(Accuracy_hue),max(Accuracy_hue),mean(Accuracy_hue),sd(Accuracy_hue),min(Accuracy_sat),max(Accuracy_sat),mean(Accuracy_sat),sd(Accuracy_sat),mean(Confidence),sd(Confidence)) %>% 
  arrange(Color_label_matched)

## Outliers
# outliers1 <- which.outlier(data$Accuracy_hue)
# outliers2 <- which.outlier(data$Accuracy_sat)
outliers_hue <- boxplot(data$Accuracy_hue, plot=FALSE)$out
outliers_sat <- boxplot(data$Accuracy_sat, plot=FALSE)$out
#remove outliers
data_no_outliers_hue<- data[-which(data$Accuracy_hue %in% outliers_hue),]
data_no_outliers_sat<- data[-which(data$Accuracy_sat %in% outliers_sat),]

## Simple models
#Hypothesis: accuracy will decrease if confidence goes up
#For hue
hue_acc_con <- lm(Accuracy_hue ~ Confidence:Gender, data = data_no_outliers_hue)
summary(hue_acc_con)
#For saturation
sat_acc_con <- lm(Accuracy_sat ~ Confidence:Gender, data = data_no_outliers_sat)
summary(sat_acc_con)

```

